\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-03-07 reviews/response.Rmd

Done.

> p15, l45: "the day before Christmas, go shopping on the Boxing day, and stay out for the fireworks on New Year's Eve.": Some of these names may not be known to non-Christian / non-British readers. List the date in parentheses, e.g., December 24, December 26, etc.

Done.

> Fig.12: "loess smooth": cite main reference

> p21, l36: "these four households are the data of colleagues of the authors." - strange sentence; rephrase

> p22, l17-35: inconsistent use of times, e.g., "before 6", "around 18", "3pm", etc. - adjust to times used in the figures and be consistent. Also adjust caption of Fig.15.

> p22, l36: "Figure 16, 17, 18 and 19" -> "Figures 16-19"

> "individually for each household": This seems to suggest that a scale from
0 to max(household_i) [but not to max(all households)] has been used. But what is this max in each of the 4 figures? The reader has no way to easily infer this. Also mention that these 4 figs are not true small multiples as the vertical scales for the 4 households differ from figure to figure.

> Fig.15: Use labels 6, 12 & 18 and extra tick marks at 0 & 24, matching Fig 3.

> p25, l3: What about April? If added here, also add to caption of Fig.19.

> p25, l14: "Anzac Day in Australia, or Thanksgiving Day in the USA,": Never mentioned before in this article. Refer back to the special events/holidays from earlier in the article.

### 2019-03-07 main.Rmd
done with revision for reviewer 3 page 4

The algorithm can also produce more complicated plots, such as boxplots. Figure \ref{fig:boxplot} uses a loess smooth line superimposed on side-by-side boxplots. It shows the distribution of hourly counts across all 43 sensors during December. The last week of December is the holiday season: people are off work on the day before Christmas (December 24), go shopping on the Boxing day (December 26), and stay out for the fireworks on New Year's Eve.

@@

The use of the calendar display is illustrated on smart meter energy usage from four households in Melbourne, Australia. Individuals can download their own data from the energy company, and these four households are the data of colleagues of the authors. The calendar display is useful to help people understand their energy use. The data contains half-hourly electricity consumption in 2017 and 2018. The analysis begins by looking at the distribution over days of week, then time of day split by work days and non-work days, followed by the calendar display to inspect the daily schedules.

@@

Figure \ref{fig:hod} shows energy consumption against time of day, separately by week day and weekend. Household 1 is an early bird, starting their day before 6 and going back home around 18 on week days. They switch air conditioning or heating on when they get home from work and keep it operating until mid-night, learned from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for  household 2 indicates that perhaps air conditioning or heating runs continuously for some periods, consuming the twice the energy as household 1. A third peak occurs around 3pm for household 3 only, likely when the kids are home from school. They also have a consistent energy pattern between week days and weekends. As for household 4, their home routine starts after 18 on week days. Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households.

@@

Figure \ref{fig:h1}, \ref{fig:h2}, \ref{fig:h3} and \ref{fig:h4} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing over household 1, we can see that their overall energy use is low. Their week day energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (December--February) in the evening and weekends. In household 2, heating keeps functioning for consecutive hours, which is evident in the mid July. In contrast, household 1 uses heating cautiously. These observations help to explain the stripes and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous plots. Household 1 is on vacation over three weeks of June, and household 2 was also away for vacation in late December and in the second week of June. Figure \ref{fig:h3} shows household 3 takes two one-month-long family trips in September until early October and in June/July. Household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

@@

```{r h4, fig.height = 7, fig.cap = "Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Three short trips were taken in October, December, and June."}
```

>>>>

The algorithm can also produce more complicated plots, such as boxplots. Figure \ref{fig:boxplot} uses a loess smooth line [@cleveland1979loess] superimposed on side-by-side boxplots. It shows the distribution of hourly counts across all 43 sensors during December. The last week of December is the holiday season: people are off work on the day before Christmas (December 24), go shopping on the Boxing day (December 26), and stay out for the fireworks on New Year's Eve.

@@

The use of the calendar display is illustrated on smart meter energy usage from four households in Melbourne, Australia. Individuals can download their own data from the energy supplier, and the data contained in the paper is made available from four colleagues of the authors. The calendar display is useful to help people understand their energy use. The data contains half-hourly electricity consumption in 2017 and 2018. The analysis begins by looking at the distribution over days of week, then time of day split by work days and non-work days, followed by the calendar display to inspect the daily schedules.

@@

Figure \ref{fig:hod} shows energy consumption against time of day, separately by week day and weekend. Household 1 is an early bird, starting their day before 6 and going back home around 18 on week days. They switch air conditioning or heating on when they get home from work and keep it operating until mid-night, learned from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for  household 2 indicates that perhaps air conditioning or heating runs continuously for some periods, consuming the twice the energy as household 1. A third peak occurs around 15 for household 3 only, likely when the kids are home from school. They also have a consistent energy pattern between week days and weekends. As for household 4, their home routine starts after 18 on week days. Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households.

@@

Figure \ref{fig:h1}-\ref{fig:h4} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing over household 1, we can see that their overall energy use is low. Their week day energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (December--February) in the evening and weekends. In household 2, heating keeps functioning for consecutive hours, which is evident in the mid July. In contrast, household 1 uses heating cautiously. These observations help to explain the stripes and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous plots. Household 1 is on vacation over three weeks of June, and household 2 was also away for vacation in late December and in the second week of June. Figure \ref{fig:h3} shows household 3 takes two one-month-long family trips in September until early October and in June/July. Household 4 is away over two or three weeks in early October, December, early April, and late June. The use of air conditioning and heating leaves no trace in these two households.

@@

```{r h4, fig.height = 7, fig.cap = "Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Three short trips were taken in October, December, April, and June."}
```

### 2019-03-07 main.tex
done with revision for reviewer 3 page 4

The algorithm can also produce more complicated plots, such as boxplots.
Figure \ref{fig:boxplot} uses a loess smooth line superimposed on
side-by-side boxplots. It shows the distribution of hourly counts across
all 43 sensors during December. The last week of December is the holiday
season: people are off work on the day before Christmas (December 24),
go shopping on the Boxing day (December 26), and stay out for the
fireworks on New Year's Eve.

@@

\caption{Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Three short trips were taken in October, December, and June.}\label{fig:h4}
\end{figure}

>>>>

The algorithm can also produce more complicated plots, such as boxplots.
Figure \ref{fig:boxplot} uses a loess smooth line
\citep{cleveland1979loess} superimposed on side-by-side boxplots. It
shows the distribution of hourly counts across all 43 sensors during
December. The last week of December is the holiday season: people are
off work on the day before Christmas (December 24), go shopping on the
Boxing day (December 26), and stay out for the fireworks on New Year's
Eve.

@@

\caption{Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Three short trips were taken in October, December, April, and June.}\label{fig:h4}
\end{figure}
